%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\setlength{\textwidth}{5.1in} % Text width of the document


%\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{tgpagella}
\usepackage{enumitem}
\usepackage[colorlinks=true]{hyperref}% \usepackage[hidelinks=true]{hyperref}
\usepackage{fancyhdr} \pagestyle{fancy} \renewcommand{\headrulewidth}{0pt}
\usepackage{dirtytalk}
\usepackage[usenames, dvipsnames]{color}


%----------------------------------------------------------------------------------------
%	CUSTOM COMMANDS
%----------------------------------------------------------------------------------------

\newcommand{\Year}[1]{\emph{#1}}
\newcommand{\uni}[1]{\textbf{#1}}
\newcommand{\eventYear}[2]{\uni{#1}\hfill{\Year{#2}}\\}

% Color the section headers
\definecolor{crimson}{RGB}{164, 16, 52}
\let\oldsection\section
\renewcommand{\section}[1]{\oldsection{\textcolor{crimson}{#1}}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}


\author{Arya D. McCarthy}
\date{\today}

% Headers
\makeatletter
\lfoot{\@author}
\cfoot{\@date}
\makeatother
\rfoot{\thepage}

% Hrefs
\newcommand{\JHU}{\href{https://www.jhu.edu/}{Johns Hopkins University}}
\newcommand{\jhu}{\href{https://www.jhu.edu/}{JHU}}
\newcommand{\SMU}{\href{https://www.smu.edu/}{Southern Methodist University}}
\newcommand{\smu}{\href{https://www.smu.edu/}{SMU}}
\newcommand{\HPHS}{\href{http://hs.hpisd.org}{Highland Park High School}}
\newcommand{\STAN}{\href{https://www.stanford.edu/}{Stanford University}}
\newcommand{\UOE}{\href{https://www.ed.ac.uk/}{University of Edinburgh}}
\newcommand{\clsp}{\href{https://www.clsp.jhu.edu}{CLSP}}
\newcommand{\CLSP}{\href{https://www.clsp.jhu.edu}{Center for Language and Speech Processing}}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft2.17\hoffset\centerline{\textsc{\LARGE Arya D. McCarthy}} % Your name at the top
 \vspace{-0.5em}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.5pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 \vspace{-2em}
\begin{resume}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\section{Contact Information}

%\noindent
\begin{minipage}{0.6180339887498949\textwidth}
  \href{https://www.cs.jhu.edu/}{Department of Computer Science}\\
  \href{https://www.jhu.edu/}{Johns Hopkins University}\\
  Hackerman 321\\
  3400 North Charles Street\\
  Baltimore, MD 21218, USA
\end{minipage}% This must go next to `\end{minipage}`
\begin{minipage}{0.3819660112501051\textwidth}
  \begin{flushright}
      Phone: \href{tel:+14698343984}{\textsc{(469) 834-3984}}\\
      \href{mailto:arya@jhu.edu}{arya@jhu.edu}\\
      \href{https://cs.jhu.edu/~arya}{cs.jhu.edu/{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}arya}
  \end{flushright}
\end{minipage}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\eventYear{\JHU}{Ongoing}
	Ph.D. in Computer Science
	\begin{description}[noitemsep, labelindent=1em]
	\item[Affiliation:] \CLSP
	\item[Advisor:] \href{http://www.cs.jhu.edu/~yarowsky/}{David Yarowsky}
	\end{description}

\eventYear{\SMU}{2017}
	M.S. in Computer Science
	\begin{description}[noitemsep, labelindent=1em]
	\item[Thesis:] \href{https://search.proquest.com/docview/1907180434?pq-origsite=gscholar}{The Leximin Method for Hierarchical Community Detection}
	\item[Advisor:] \href{https://lyle.smu.edu/~matula/}{David W. Matula}
	\end{description}
 
\eventYear{\SMU}{2017}
	B.S. in Computer Science, Mathematics
	\begin{description}[noitemsep, labelindent=0.5em]
	\item Magna Cum Laude; \href{http://www.smu.edu/dedman/studentresources/universityhonors}{Honors in the Liberal Arts, University Honors Program}
	\end{description}
	
%\eventYear{\HPHS}{2013}
%	Valedictorian
	
\emph{Single terms of study at the \UOE{} (2015) and \STAN{} (2014)}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT SECTION
%----------------------------------------------------------------------------------------


\section{Employment}

\eventYear{\href{https://hltcoe.jhu.edu/research/scale/scale-2018/}{SCALE 2018}}{June -- August 2018}
Machine Translation Researcher
\begin{description}[nosep]
\item[Host:] \href{http://cs.jhu.edu/~kevinduh/}{Kevin Duh, Ph.D.}
\end{description}

\begin{samepage}
\eventYear{\href{https://www.smu.edu/Lyle/Institutes/DeasonInstitute}{Darwin Deason Institute for Cyber Security}}{October 2015 -- May 2016}
Research Assistant
\begin{description}[nosep]
\item[Host:] \href{https://s2.smu.edu/~mitch/}{Mitch Thornton, Ph.D.}
\end{description}
\end{samepage}

%----------------------------------------------------------------------------------------
%	GRANTS SECTION
%----------------------------------------------------------------------------------------

\section{Fellowships}

\textbf{\href{http://www.smu.edu/Dedman/DCII/Programs/Mayer}{Robert Mayer Interdisciplinary Fellowship}}
\begin{description}[nosep, labelindent=1em]
\item[Awarding body:] \href{http://www.smu.edu/Dedman/DCII}{SMU Dedman College Interdisciplinary Institute}
\item[Amount:] \$1,500
\item[Supervisor:] \href{http://faculty.smu.edu/snorris/}{Scott Norris, Ph.D.} and \href{https://www.smu.edu/News/Experts/Matthew-Wilson}{Matthew Wilson, Ph.D.}
\item Coming Together, Mathematically: Dynamical Models for Increased Uniformity and Polarization in American Politics.
\end{description}

\begin{samepage}
\textbf{\href{http://www.smu.edu/Dedman/DCII/Programs/Hamilton}{Hamilton Undergraduate Research Fellowship}}
\begin{description}[nosep, labelindent=1em]
\item[Awarding body:] \SMU
\item[Amount:] \$3,000
\item[Supervisor:] \href{http://faculty.smu.edu/snorris/}{Scott Norris, Ph.D.}
\item Implemented and extended waveform relaxation solver for modeling interrelated differential equations without loss of accuracy.
\end{description}
\end{samepage}


\textbf{\href{https://uraf.harvard.edu/amgen-scholars}{Harvard--Amgen Scholarship}}
\begin{description}[nosep, labelindent=1em]
\item[Awarding body:] \href{https://uraf.harvard.edu/home}{Harvard University}; \href{http://www.amgen.com/responsibility/amgen-foundation/}{Amgen Foundation}
\item[Amount:] \$4,500
\item[Supervisor:] \href{http://www.eecs.harvard.edu/shieber/}{Stuart Shieber, Ph.D.}
\item Toward coreference resolution shared task, adapted multithreaded feature extraction code in Java to serialize and deliver features to Torch neural network.
\end{description}

\vspace{10em}
%----------------------------------------------------------------------------------------
%	TEACHING SECTION
%----------------------------------------------------------------------------------------

\section{Teaching}

\begin{samepage}
\eventYear{\SMU}{Spr., Sum., Fall 2018}
\href{https://datascience.smu.edu/academics/curriculum/coursedescriptions/#data-science}{Doing Data Science (MSDS 6306)}
\begin{description}[noitemsep, labelindent=1em]
\item[Role:] Teaching Assistant
\item[Professor:] Faizan Javed
\item For two sections, I assisted weekly synchronous sessions and graded reports in SAS, Python, and R. Part of SMU's Master's of Science in Data Science program.
\end{description}
\end{samepage}

\begin{samepage}
\eventYear{\SMU}{Fall 2017}
\href{https://datascience.smu.edu/academics/curriculum/coursedescriptions/#quantifying}{Quantifying the World (MSDS 7333)}
\begin{description}[noitemsep, labelindent=1em]
\item[Role:] Grader
\item[Professor:] Owen Martin, John Verostek
\end{description}
\end{samepage}

\begin{samepage}
\eventYear{\SMU}{Fall 2014}
\href{https://tylermoore.ens.utulsa.edu/courses/cse3353/}{Fundamentals of Algorithms (CSE 3353)}
\begin{description}[noitemsep, labelindent=1em]
\item[Role:] Teaching Assistant
\item[Professor:] \href{https://tylermoore.ens.utulsa.edu}{Tyler Moore, Ph.D.}
\item Led 2 office hours weekly, answered questions via Piazza, and graded all assignments and exams for 30 students.
\end{description}
\end{samepage}



%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\begin{itemize}
\item \href{https://www.smu.edu/Academics/PS}{President's Scholarship}. Highest merit scholarship at SMU\@. Full tuition, funded study abroad, and dinners with Tate Lecture speakers. One of 21 in class of 2017.
\item \href{https://www.smu.edu/Academics/PS/Benefits}{Campus Community Award}. Full room and board scholarship awarded for leadership and impact on campus. Approximately 90 chosen each year.
\item \href{https://www.smu.edu/EnrollmentServices/Registrar/AcademicCeremonies/HonorsConvocation/HonorSocieties}{Robert S. Hyer Society}. Highest academic honor at SMU\@. One of 12 juniors selected in 2016.
\item \href{https://www.smu.edu/EnrollmentServices/Registrar/AcademicCeremonies/HonorsConvocation/AwardRecipients}{Charles J. Pipes Award for Outstanding Performance in Mathematics}. One chosen each year.
\item Dean's Award. Best CSE poster at \href{http://www.smu.edu/graduate/CurrentStudents/ResearchDay}{SMU Research Day 2017}: Nibhrat Lohia, Raunak Mundada, \textbf{Arya D. McCarthy}. \emph{AirWare: An Advanced In-Air Hand-Gesture Recognition System Using Ultrasonic Doppler Signatures Leveraging Deep Neural Network Architectures}.
\item Tau Beta Pi (as sophomore)
\item Upsilon Pi Epsilon (as junior)
\end{itemize}

 %----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Publications}
\textbf{Refereed Conference Papers}

\begin{enumerate}
\item Brian Thompson, Huda Khayrallah, Antonios Anastasopoulos, \textbf{Arya D. McCarthy}, Kevin Duh, Rebecca Marvin, Paul McNamee, Jeremy Gwinnup, Tim Anderson and Philipp Koehn. 2018. Freezing Subnetworks to Analyze Domain Adaptation in Neural Machine Translation. In \emph{Proceedings of the Conference on Machine Translation (WMT)}, Brussels, Belgium. ACL. \emph{(To appear)}

\item Christo Kirov, Ryan Cotterell, John Sylak-Glassman, G\'eraldine Walther, Ekaterina Vylomova, Patrick Xia, Manaal Faruqui, \textbf{Arya D. McCarthy}, Sandra K{\"u}bler, David Yarowsky, Jason Eisner, and Mans Hulden. 2018. \href{http://www.lrec-conf.org/proceedings/lrec2018/pdf/789.pdf}{UniMorph 2.0: Universal Morphology}. In \emph{Proceedings of the Ninth International Conference on Language Resources and Evaluation (LREC)}. European Language Resources Association (ELRA).
\end{enumerate}

\filbreak

\textbf{Refereed Workshop Proceedings}
\begin{enumerate}[resume]
\item \textbf{Arya D. McCarthy}, Miikka Silfverberg, Mans Hulden, David Yarowsky and Ryan Cotterell. 2018. Marrying Universal Dependencies and Universal Morphology. In \emph{Proceedings of the EMNLP 2018 Workshop on Universal Dependencies (UDW 2018)}, Brussels, Belgium. ACL. \emph{(To appear)}

\item \textbf{Arya D. McCarthy} and David W. Matula. 2018. \href{https://cloud.skewed.de/index.php/s/ypEW2ym8JkeaZ8p#pdfviewer}{Normalized mutual information exaggerates community detection performance}. In \emph{SIAM Workshop on Network Science}, Portland, OR, USA. Society for Industrial and Applied Mathematics.
\end{enumerate}

\filbreak
\textbf{Non-Public Technical Reports}
\begin{enumerate}[resume]
\item \textbf{Arya D. McCarthy}. 2016. Design and Implementation of a Method of Abstractly Simulating Cyber Security Vulnerabilities: Embedded Markov and Discrete Event Simulation Approaches. \emph{Deason Institute for Cyber Security.}
\end{enumerate}

\filbreak
\textbf{Non-Refereed}
\begin{enumerate}
\item \textbf{Arya D. McCarthy}, Scott A. Norris. 2017. Toward Fast, Accurate Simulation of Gap Junctions in NNs. \emph{National Collegiate Research Conference.} (Abstract)
\item \textbf{Arya D. McCarthy}, Sam Wiseman, Stuart Shieber. 2015. Toward Multilingual Neural Coreference Resolution. \emph{Harvard--Amgen Scholars Program.} (Abstract)
\end{enumerate}


%----------------------------------------------------------------------------------------
%	INVITED TALKS SECTION
%----------------------------------------------------------------------------------------

\section{Invited Talks}
\begin{enumerate}
\item Coming Together, Mathematically: Dynamical Models for \hfill \Year{May 2017}\\
 Increased Uniformity and Polarization in American Politics. \\
Location: Southern Methodist University (Hamilton Fellows Series)\\
Host: Kathleen Hugley-Cook
\item Toward Fast, Accurate Simulation of Gap Junctions in NNs. \hfill \Year{March 2017}\\
Location: Southern Methodist University (as Summer Research Fellow)\\
Host: Robert Kehoe
\end{enumerate}

 %----------------------------------------------------------------------------------------
%	SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{Service}

\textbf{Shared Task Organizer}

\begin{itemize}
\item \href{https://sigmorphon.github.io/sharedtasks/2018/}{CoNLL--SIGMORPHON 2018 Shared Task: Cross-Lingual Morphological Reinflection}

\end{itemize}

\textbf{Professional Service}

\begin{itemize}[noitemsep]
\item Program Committee,  \href{https://sigmorphon.github.io}{SIGMORPHON} (\href{https://sigmorphon.github.io/workshops/2018/}{2018})
\item Reviewer: WMT (\href{http://www.statmt.org/wmt18/}{2018}), EMNLP (2018 secondary)
\item Open-source contributions: \href{http://networkx.github.io}{\texttt{networkx}}, \texttt{PyTorch}, \texttt{scikit-learn}, \texttt{OpenNMT-py}
\item Webmaster: \href{https://sigmorphon.github.io}{ACL SIGMORPHON}, \href{https://unimorph.github.io}{UniMorph morphology project}, \href{http://ubicomp.lyle.smu.edu}{SMU Ubiquitous Computing Lab} (2016--2017)
\item Founder and editor-in-chief, \href{https://smuresearch.wordpress.com/journal/}{\emph{SMU Journal of Undergraduate Research}} (2014--2017)
\item Editor-in-chief, \href{https://smuresearch.wordpress.com/kairos/}{\emph{Kairos}} interdisciplinary magazine (2015--2016)
\end{itemize}

% \subsection{Community Service}

\textbf{University Service}

\begin{itemize}[noitemsep]
\item Judge for \href{https://en.wikipedia.org/wiki/ACM_International_Collegiate_Programming_Contest}{ACM-ICPC} contest at JHU
\item Diversity and Inclusion Committee for \href{https://www.cs.jhu.edu}{Department of Computer Science}
\item Faculty Liaison Committee for \clsp
\item Vice-President, SMU Tau Beta Pi (2016--2017)
\item President, SMU Upsilon Pi Epsilon (2015--2017)
\item Sole student member of SMU Undergraduate Research Steering Committee
\item Common Reading selection committee, SMU
\end{itemize}

%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------

\section{References}

\begin{description}[noitemsep]
\item[David Yarowsky] (\href{mailto:yarowsky@jhu.edu}{yarowsky@jhu.edu}), \JHU
\item[Ryan Cotterell] (\href{mailto:rcotter2@jhu.edu}{rcotter2@jhu.edu}), Cambridge University
\item[David W. Matula] (\href{mailto:matula@smu.edu}{matula@smu.edu}), \SMU
\item[Scott A. Norris] (\href{mailto:snorris@smu.edu}{snorris@smu.edu}), \SMU
\item[Eric C. Larson] (\href{mailto:eclarson@smu.edu}{eclarson@smu.edu}), \SMU
\item[Daniel W. Engels] (\href{mailto:dwe@alum.mit.edu}{dwe@alum.mit.edu}), \SMU
\end{description}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\begin{description}
\item[Formal Languages:] Python, R, SAS, \CPP, SQL, Objective-C, Java, JavaScript, MATLAB, \LaTeX
\item[Machine Learning Frameworks:] PyTorch, scikit-learn, TensorFlow
\item[Natural Languages:] English, Farsi, Spanish, Italian, Romanian (written); basic Dutch and German
\item[Graduate-Level Coursework in Computer Science:] Linguistic \& Sequence Modeling, Machine Translation, Machine Learning in Python, Data Mining, Algorithm Engineering, Computer Architecture
\item[Graduate-Level Coursework in Mathematics and Statistics:] Bayesian Statistics, Linear Programming, Data Science, Numerical Methods I (numerical linear algebra) and II (numerical analysis), Mathematical Models in Biology
\end{description}

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{Extracurricular Activities} 

Bagpiper \\
Ballroom Dancer% \\
%If my first NLP paper is accepted to EMNLP 2018, I \emph{will} wear my kilt.

%----------------------------------------------------------------------------------------

\end{resume}

\end{document}